\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[shortlabels]{enumitem}
\usepackage{hyperref}
\usepackage{xurl}
\input{release_info.tex}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\title{Digital Calibration Note for OPH Screen Microphysics:\\
The Octahedral \(\mathbb Z_2/S_3\) Patch Simulator}
\author{B.\ M\"uller \and Kai Xue}
\date{\OPHPaperReleaseDate}

\begin{document}
\maketitle
\OPHPaperReleaseBanner

\begin{abstract}
This note defines the octahedral \(\mathbb Z_2/S_3\) simulator ladder as a digital calibration
surface. The simulator gives an exact finite patch cover, explicit overlap collars, controlled
defects, record writes, repair schedules, edge-sector labels, and negative controls. Its scope is
fixed-cutoff interface logic and sphere-geometry charts. OPH's physical microphysics is the
federated patch-carrier picture developed in the companion microphysics paper; this simulator is a
calibration surface.
\end{abstract}

\section{Reading Rule}

The microphysics paper
\emph{Federated Echosahedral Screen Microphysics: Patch Hardware, Records, and Observer
Synchronization in OPH} treats the spherical screen as an observer-facing regulator chart and
the implementation surface as a federation of finite observer patches.

This note has a narrower role:
\begin{enumerate}[leftmargin=2em]
\item validate finite patch, overlap, record, and repair bookkeeping;
\item test frustrated-cycle and defect behavior in an exact digital setting;
\item calibrate the edge-sector law on a finite declared interface;
\item provide reproducible benchmark names and run-manifest expectations;
\item avoid any claim that the digital sphere is the literal OPH substrate.
\end{enumerate}

\section{Octahedral Patch Cover}

Use the octahedral cellulation of \(S^2\) as a small digital regulator chart. Label vertices
\[
X_+,\ X_-,\ Y_+,\ Y_-,\ Z_+,\ Z_-.
\]
The graph has twelve edges and eight triangular faces. The patch cover is the three-patch cover
\[
P_X,\qquad P_Y,\qquad P_Z,
\]
where \(P_X\) contains the faces incident on \(X_+\) or \(X_-\), and similarly for \(P_Y\) and
\(P_Z\). The pairwise overlaps are denoted
\[
B_{XY},\qquad B_{XZ},\qquad B_{YZ}.
\]

The cover is intentionally small. It is large enough to expose pairwise overlaps, repair
schedules, and a frustrated cycle, while remaining small enough for exact state and log
inspection.

\section{\(\mathbb Z_2\) Pilot}

The first digital pilot uses \(G=\mathbb Z_2\). Each oriented link carries one bit or one qubit
in the computational basis. The local gauge constraint is the even-parity constraint on incident
links. Face holonomies are mod-two sums around triangular faces.

The pilot contains:
\begin{enumerate}[leftmargin=2em]
\item link registers on the twelve octahedral edges;
\item face-holonomy readouts;
\item one coarse cut bit for each active overlap;
\item record registers for patch-local write/compare/verify events;
\item a finite repair menu that flips declared collar links when doing so lowers the mismatch
score without violating the local acceptance rule.
\end{enumerate}

The \(\mathbb Z_2\) pilot is the abelian sanity surface. It should pass clean synchronization
cases, expose stale records, repair single collar flips, and refuse to hide frustrated cycles.

\section{\(S_3\) Upgrade}

The first nonabelian upgrade keeps the octahedral graph and patch cover. The cut bit becomes an
encoded \(S_3\) register. Each group element is encoded in three bits with an invalid-word
penalty. The vertex projector is
\[
P_v^{S_3}=\frac{1}{6}\sum_{h\in S_3}U_v(h),
\]
where \(U_v(h)\) is the local left/right action on links incident to \(v\).

The upgrade tests:
\begin{enumerate}[leftmargin=2em]
\item nonabelian orientation bookkeeping;
\item conjugacy-class sector labels;
\item invalid-word penalties;
\item noncommuting defect order;
\item class-sensitive edge-sector readout.
\end{enumerate}

Passing the \(S_3\) suite does not prove compact-gauge reconstruction. It only shows that the
fixed-cutoff interface can carry nonabelian labels and record their repair behavior without
collapsing to the abelian pilot.

\section{Benchmark Families}

The named calibration gates are:
\begin{enumerate}[leftmargin=2em]
\item \texttt{Z2-0-clean}: initialize the \(\mathbb Z_2\) pilot in the clean sector and verify
stable synchronization.
\item \texttt{Z2-1-stale-record}: flip one stored record after a write layer and require the
next compare/repair cycle to expose it.
\item \texttt{Z2-2-collar-flip}: inject one collar-edge flip before compare and require local
repair.
\item \texttt{Z2-3}: double-overlap test. Inject two collar defects on different overlaps and test
schedule-insensitive repair.
\item \texttt{Z2-4}: frustrated-cycle test. Inject a cyclic obstruction and require the simulator
not to fake global agreement.
\item \texttt{S3-0-clean}: initialize the \(S_3\) build in the declared identity sector.
\item \texttt{S3-1-transposition}: inject a transposition-class defect.
\item \texttt{S3-2-threecycle}: inject a three-cycle defect.
\item \texttt{S3-3-mixed-class-cycle}: inject mixed nonabelian class data around the cycle and
require class-sensitive failure reporting.
\end{enumerate}

\section{Run Manifest}

Each digital run should write a manifest containing:
\begin{enumerate}[leftmargin=2em]
\item benchmark name and simulator commit;
\item graph, patch cover, group, encoding, and invalid-word policy;
\item repair weights, tie-break rule, and schedule;
\item per-cycle link state, face holonomies, overlap labels, record values, mismatch score, and
repair move;
\item final normal form or obstruction report;
\item pass/fail decision with declared failure class.
\end{enumerate}

The manifest is a digital analogue of the hardware evidence-bundle rule. It makes calibration
claims auditable without confusing them with hardware evidence.

\section{Negative Controls}

Mandatory negative controls include:
\begin{enumerate}[leftmargin=2em]
\item stale-record control: disable record refresh and require the stale-record benchmark to fail;
\item wrong-orientation control: reverse one \(S_3\) edge orientation and require a nonabelian
failure signature;
\item no-illegal-penalty control: set the invalid-word penalty to zero and require failure in the
\(S_3\) suite;
\item fake-repair control: allow repair moves that rewrite records without touching overlap data
and require the exact compare log to reject the run.
\end{enumerate}

\section{Boundary}

This calibration note supports the fixed-cutoff theorem interface by making it executable in a
small finite regulator chart. It does not identify the unique OPH UV completion, does not carry
hardware evidence, does not prove the Yang--Mills repair-gap theorem, and does not promote
source-only hadron predictions.

\end{document}
